%%%%%%%%% MASTER -- compiles the 4 sections

\documentclass[11pt,letterpaper]{article}


\setcounter{secnumdepth}{0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{plain}                                                      %%
%%%%%%%%%% EXACT 1in MARGINS %%%%%%%                                   %%
\setlength{\textwidth}{6.5in}     %%                                   %%
\setlength{\oddsidemargin}{0in}   %% (It is recommended that you       %%
\setlength{\evensidemargin}{0in}  %%  not change these parameters,     %%
\setlength{\textheight}{8.5in}    %%  at the risk of having your       %%
\setlength{\topmargin}{0in}       %%  proposal dismissed on the basis  %%
\setlength{\headheight}{0in}      %%  of incorrect formatting!!!)      %%
\setlength{\headsep}{0in}         %%                                   %%
\setlength{\footskip}{.5in}       %%                                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                   %%
\newcommand{\required}[1]{\section*{\hfil #1\hfil}}                    %%
\renewcommand{\refname}{\hfil References Cited\hfil}                   %%
\bibliographystyle{plain}                                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{epsfig}
\usepackage{url}

% \newcommand{\cello}{\textsf{Cello}}
% \newcommand{\enzo}{\textsf{Enzo}}
% \newcommand{\enzoii}{\textsf{Enzo}-\texttt{II}}
% \newcommand{\lcaperf}{\textsf{lcaperf}}
% \newcommand{\lcatest}{\textsf{lcatest}}
% 
% \newcommand{\pp}{\texttt{++}}
% \newcommand{\cpp}{C\pp}
% \newcommand{\charm}{\textsf{Charm\pp}}
% \newcommand{\chombo}{\textsf{Chombo}}
% \newcommand{\samrai}{\textsf{SAMRAI}}
% \newcommand{\paramesh}{\textsf{PARAMESH}}
% \newcommand{\gadget}{\textsf{GADGET}}
% \newcommand{\alps}{\textsf{ALPS}}
% \newcommand{\clawpack}{\textsf{CLAWPACK}}
% \newcommand{\grace}{\textsf{GrACe}}
% \newcommand{\carpet}{\textsf{Carpet}}
% \newcommand{\flash}{\textsf{FLASH}}
% 
% \newcommand{\code}[1]{\textsf{#1}}
% 
% \newcounter{figctr}
% 
% \newcommand{\FIGURE}[3]{
% \noindent
% \parbox{\textwidth}{
% %\ \\ \hrule \ \\
% \begin{center}
% #3
% \end{center}%
% \ \nolinebreak%
% \refstepcounter{figctr}%
% \begin{center}%
% \begin{minipage}{7.0in}
% \textbf{Figure \thefigctr}. #1
% \end{minipage}
% \end{center}
% \label{#2}
% %\ \\ \hrule \ \\
% }}

\include{newcommand}

% NSF proposal generation template style file.
% based on latex stylefiles  written by Stefan Llewellyn Smith and
% Sarah Gille, with contributions from other collaborators.

\DeclareFontFamily{OT1}{psyr}{}
\DeclareFontShape{OT1}{psyr}{m}{n}{<-> psyr}{}
\def\times{{\fontfamily{psyr}\selectfont\char180}}


\renewcommand{\refname}{\centerline{References cited}}

% this handles hanging indents for publications
% \def\rrr#1\\{\par
%\medskip\hbox{\vbox{\parindent=2em\hsize=6.12in
%\hangindent=4em\hangafter=1#1}}}

\def\baselinestretch{1}

 \addtolength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
\textbf{\large{James O. Bordner}} \\
San Diego Supercomputer Center \\
University of California, San Diego \\
jobordner@ucsd.edu \\
\end{center}

\subsection{Professional Preparation}
\begin{tabular}{lll}
University of Illinois, Urbana-Champaign &  Computer Science & B.S.~1990 \\
University of Illinois, Urbana-Champaign & Computer Science  & M.S.~1995 \\
University of Illinois, Urbana-Champaign & Computer Science  & Ph.D.~1999 \\
University of Illinois, Urbana-Champaign & Computational Science  & Postdoc, 1999-2000 \\
University of California, San Diego      & Computational Science  & Postdoc, 2000-2005
\end{tabular}
\subsection{Appointments}
\begin{tabular}{ll}
2005-present & Assistant Project Scientist, University of California, San Diego
\end{tabular}

\subsection{Publications}

\subsubsection{Selected relevant publications}
\begin{enumerate}
\item Norman, M.L., G.~Bryan, R.~Harkness, J.~Bordner, D.~Reynolds, B.~O'Shea, R.~Wagner, 
      ``Simulating Cosmological Evolution with Enzo,''
      Petascale Computing: Algorithms and Applications,
      chapman \& Hall/CRC Computational Science,
      2007.
\item Bordner, J.O., A.~Kritsuk, M.~Norman, R.~Weaver, ``Comparing Parallel CAMR and SAMR Hydrodynamic Simulations,''
      University of California, San Diego, Center for Astrophysics \& Space Sciences Technical Report, 
      2005.  \url{http://lca.ucsd.edu/~jbordner/enzo-sage.ps}
\item Bordner, J.O., 
      ``Toward Optimizing Enzo, an AMR Cosmology Application,'' 
      Adaptive Mesh Refinement---Theory and Applications, 
      Lecture Notes in Computational Sciences and Engineering, 
      Springer-Verlag, 
      2004.
\item O'Shea, B.W., G.~Bryan, J.~Bordner, M.L.~Norman, T.~Abel, R.~Harkness, A.~Kritsuk, 
      ``Introducing Enzo, an AMR Cosmology Application,'' 
      Adaptive Mesh Refinement Theory and Applications, 
      Lecture Notes in Computational Sciences and Engineering, 
      Springer Verlag, 
      2004.
\item Bordner, J.O., ``Using MGMPI'',
      University of California, San Diego, Center for Astrophysics \& Space Sciences Technical Report, 
      2003.  \url{http://lca.ucsd.edu/~jbordner/mgmpi-user.pdf}
\end{enumerate}

\subsubsection{Other selected publications}

\begin{enumerate}
\item Hayes, J.C., M.L.~Norman, R.A.~Fiedler, J.O.~Bordner, P.S.~Li, S.E.~Clark, A.~ud-Doula, M.-M.~Mac Low, Simulating Radiating and Magnetized Flows in Multi-Dimensions with ZEUS-MP,'' Ap.~J.~Supp., 165, 188--228, 2006.  \url{http://www.iop.org/EJ/article/0067-0049/165/1/188/63995.web.pdf}
\end{enumerate}

\subsection{Synergistic Activities}

\begin{enumerate}
\item Developed and provides user support for \code{lcatest}, an automated testing environment for parallel software.
\item Developed and provides user support for \code{lcaperf}, a software API and associated utilities for measuring and analysing performance of complex parallel applications.
\item Developed \code{MGMPI}, a parallel multigrid software library.
\item Contributed to the development and testing of the parallel astrophysics and cosmology application \code{Enzo}, including adding support for linear solves on its AMR hierarchy using the \code{hypre} package, adding support for measuring
and analysing the parallel performance of \code{Enzo}, and refactoring
\code{Enzo}'s AMR data structures to improve memory usage, performance, and scaling.
\end{enumerate}

\subsubsection{Advisors}

Ph.D.: Faisal Saied (Purdue) \\
Postdoc: Michael L. Norman (UCSD)

\subsubsection{Graduate students}
None
\subsubsection{Postdocs}

None

\subsubsection{Collaborators}

Collins, D.~(UCSD), 
Harkness, R.~(SDSC), 
Hayes, J.~(LLNL), 
Kritsuk, A.~(UCSD), 
Norman, M.L.~(UCSD), 
O'Shea, B.W.~(MSU), 
Paschos, P.~(UCSD), 
Reynolds, D.~(SMU), 
Wagner, R.~(SDSC)

\end{document}
