%%%%%%%%% MASTER -- compiles the 4 sections

\documentclass[11pt,letterpaper]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{plain}                                                      %%
%%%%%%%%%% EXACT 1in MARGINS %%%%%%%                                   %%
\setlength{\textwidth}{6.5in}     %%                                   %%
\setlength{\oddsidemargin}{0in}   %% (It is recommended that you       %%
\setlength{\evensidemargin}{0in}  %%  not change these parameters,     %%
\setlength{\textheight}{8.5in}    %%  at the risk of having your       %%
\setlength{\topmargin}{0in}       %%  proposal dismissed on the basis  %%
\setlength{\headheight}{0in}      %%  of incorrect formatting!!!)      %%
\setlength{\headsep}{0in}         %%                                   %%
\setlength{\footskip}{.5in}       %%                                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                   %%
\newcommand{\required}[1]{\section*{\hfil #1\hfil}}                    %%
\renewcommand{\refname}{\hfil References Cited\hfil}                   %%
\bibliographystyle{plain}                                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{epsfig}
\usepackage{url}

\newcommand{\cello}{\textsf{Cello}}
\newcommand{\enzo}{\textsf{Enzo}}
\newcommand{\enzoii}{\textsf{Enzo}-\texttt{II}}
\newcommand{\lcaperf}{\textsf{lcaperf}}
\newcommand{\lcatest}{\textsf{lcatest}}

\newcommand{\pp}{\texttt{++}}
\newcommand{\cpp}{C\pp}
\newcommand{\charm}{\textsf{Charm\pp}}
\newcommand{\chombo}{\textsf{Chombo}}
\newcommand{\samrai}{\textsf{SAMRAI}}
\newcommand{\paramesh}{\textsf{PARAMESH}}
\newcommand{\gadget}{\textsf{GADGET}}
\newcommand{\alps}{\textsf{ALPS}}
\newcommand{\clawpack}{\textsf{CLAWPACK}}
\newcommand{\grace}{\textsf{GrACe}}
\newcommand{\carpet}{\textsf{Carpet}}
\newcommand{\flash}{\textsf{FLASH}}

\newcommand{\code}[1]{\textsf{#1}}

\newcounter{figctr}

\newcommand{\FIGURE}[3]{
\noindent
\parbox{\textwidth}{
%\ \\ \hrule \ \\
\begin{center}
#3
\end{center}%
\ \nolinebreak%
\refstepcounter{figctr}%
\begin{center}%
\begin{minipage}{7.0in}
\textbf{Figure \thefigctr}. #1
\end{minipage}
\end{center}
\label{#2}
%\ \\ \hrule \ \\
}}

% NSF proposal generation template style file.
% based on latex stylefiles  written by Stefan Llewellyn Smith and
% Sarah Gille, with contributions from other collaborators.

\DeclareFontFamily{OT1}{psyr}{}
\DeclareFontShape{OT1}{psyr}{m}{n}{<-> psyr}{}
\def\times{{\fontfamily{psyr}\selectfont\char180}}


\renewcommand{\refname}{\centerline{References cited}}

% this handles hanging indents for publications
\def\rrr#1\\{\par
\medskip\hbox{\vbox{\parindent=2em\hsize=6.12in
\hangindent=4em\hangafter=1#1}}}

\def\baselinestretch{1}

% \setcounter{secnumdepth}{2}

%-----------------------------------------------------------------------
% NSF
%-----------------------------------------------------------------------
%
% FIVE SOFTWARE FOCUS AREAS
%
%  * 1. software for HPC systems
%    2. software for digital data management
%    3. software for broadband and networking
%    4. middleware
%    5. cybersecurity
%
% CROSS CUTTING ISSUES
%
%  * software sustainability
%
%  * software self-manageability
%
%  - software power/energy efficiency
%
%
% HPC SOFTWARE ISSUES
%
%  * deep-memory hierarchies
%  * multi-core architectures
%  * heterogeneous/hybrid systems
%  * architecture agnostic
%
% SDCI REQUIREMENTS
%
%  * identify software focus area and category in title
%  * support for at least one cross-cutting issue
%  * identify multiple application areas in science or engineering
%    - missing capability required
%    - specific examples of how tool will impact science research
%  * clear description of how approach compares to existing approaches
%  * explicit outreach and education plan for additional end user groups
%  * explicit description of the engineering process used
%    - design, development, release, deployments, tool interoperability,
%    - evaluation plan that includes end users [ref nmi.cs.wisc.edu]
%  * list of tangible metrics to measure success, with end users
%    - quantitative + qualitative definition of "working prototype"
%    - steps from prototype to production use
%  * compelling discussion of software's potential use by broader communities
%    - use cases with relevant domain scientists
%  * sustainability plan beyond the award lifetime
%  * identify open source licence
%    
%-----------------------------------------------------------------------


% Project summary
% Introduction
%    Extreme parallelism
%    Extreme AMR
%    Existing AMR frameworks
%       PARAMESH
%       Chombo
%       SAMRAI
%       GADGET
% Software requirements
% Software design
%    High level components
%    Data structures
%       Patch coalescing  for ``shallow'' AMR
%       Targeted refinement with backfill for ``deep'' AMR
%    Task scheduling
%    Load balancing
% Implementation
%    Parallelism
%    Fault tolerance
%    Software implementation
% Development plan
% Milestones and deliverables

\usepackage{natbib}

\newcommand{\delete}[1]{}

%=======================================================================

\begin{document}

\textbf{Project Summary}
%
% Cello + Enzo-II
%
%   formalization of Enzo-P development as a physics application built
%   on a new independent extreme AMR framework
%
This project proposes to develop a new parallel software framework for
developing multiscale science simulations, in particular those that
require the enormous computing power of HPC platforms as they evolve
through the petascale era and into the exascale.

 multiscale scienceadaptive
mesh refinement (AMR) 
%
A distinguishing characteristic relative to existing AMR frameworks is
the aggressive pursuit at the onset of extreme scalability, in terms
of both software data structures and hardware parallelism.
%

Development and design will be approached with software sustainability
in mindThe design will be forward-looking, targeting not just the
% The proposed AMR framework would enable application
% developers to write multiphysics applications for simulating phenomena
% on an unprecedented range of spacial and temporal scales.

AMR will be implemented using a modified octree-based approach.  Nodes
of an octree will be associated with both logically Cartesian grid
blocks and groups of particles, for Eulerian, Lagrangian, and hybrid
methods for solving coupled hyperbolic, elliptic, and parabolic PDE's.
Unlike standard octree-based AMR, grid block sizes may vary, and
individual blocks may be distributed, such that optimal ``unigrid''
parallel performance is recovered in subregions of the problem domain
that are smooth.  Additionally, higher refinement factors, such as
$r=4$ or even $r=8$, will be supported for particularly ``deep'' AMR
problems; this will be designed in a way that still maintains at most
$r=2$ level jumps, and will retain the high efficiency of the octree
data structure.

Parallelization will be primarily data parallel, with task
parallelization also available to augment the data parallelism.  A
variety of parallelization technologies will be supported from the
start, beginning with the message-driven processor virtualization
approach provided by the
\charm\ framework~\cite{KaBo07}~\cite{wwwcharm}.  Other
parallelization methods used will include one-sided message passing
via the MPI-2.0 library~\cite{wwwmpi}, the partitioned global address
space (PGAS) approach via the UPC language~\cite{wwwupc}~\cite{upc},
and shared memory parallel programming using the OpenMP
API~\cite{wwwopenmp}.  Hybrid parallelism will be supported, including
MPI with OpenMP and UPC with MPI.  Dynamic load balancing of parallel
tasks will include hierarchical methods, which will improve mapping
the distributed software data structures to the hierarchical hardware
components of HPC platforms.

Fault tolerance and software resilience are also crucial factors at
extreme scales.  The checkpoint-to-disk paradigm is known to be
ultimately non-scalable, so this project will support other alternatives,
including checkpoint-to-memory, or other options as they become
technologically feasible.  Our framework will be designed at the onset
to be resistant to memory, compute component, network, disk, and
software failures.

This project plans to make the framework and accompanying documentation freely
available for use by the research community.  The result of this
project will be a software framework that allows application
developers to write multiphysics applications for simulating phenomena
on an unprecedented range of spacial and temporal scales for many
years to come.

% The proposed AMR framework would enable application
% developers to write 
\textbf{intellectual merit}

\textbf{broader impact}

\end{document}

%==================================================================

